\vspace{-2cm} \LARGE Divergence-Free Smoothed Particle Hydrodynamics \\ \large Advanced Simulation and Visualization of Fluids in Computer Graphics

### 2016-12-14 report/paper.tex
hopefully finished with background

    %A ghost fluid approach for free surface and solid boundary conditions for a SPH fluid simulation what proposed by Schechter et al.~\cite{ghost}.

>>>>

    A ghost fluid approach for free surface and solid boundary conditions for a SPH fluid simulation what proposed by Schechter et al.~\cite{ghost}.
    The ghost particles are placed on free surfaces and at solid boundary conditions.
    The approach solves problems like spurious numerical surface tension artifacts and errors in the mass conservation constraints.
